Compararison of analytical and artificial neural network models in predicting hot deformation behavior of AISI P20 and interpolation-extrapolation capacity validation

### 2022-11-09 Article.tex
Update of main tex

The procedure used for the determination of the parameters of the Johnson-Cook law is in accordance with the one proposed by He \eal \cite{He-2013}.
This method allows obtaining one after the other the $5$ parameters in the order $A$, $B$, $n$, $C$ and $m$.
Thus, according to the experimental data, the initial elastic limit of the material at the reference strain rate and reference temperature is $A=11.758$~MPa.
For the determination of the constants $B$ and $n$, from the results of the compression test at $T_0$ and $\mdot\varepsilon_0$, it is then possible to determine these two constants by considering only the first term $\left(A+B\varepsilon^{p^{n}}\right)$ in Equation (\ref{eq:Johnson-Cook}).
Thus, here, $B=25.563$~MPa and $n=0.139$.
Once the parameters $A$, $B$ and $n$ are known, the determination of $C$, considering all the curves at $T=T_0$ then gives $C=0.338$.
Finally, the last parameter $m$ is identified from the curves at $\mdot\varepsilon=\mdot\varepsilon_0$ and from the knowledge of the previous and gives $m=0.730$.
All parameters of the Johnson-Cook model are reported in Table \ref{tab:JCparams}.

\begin{table}[h!]
\centering
\caption{Parameters' values of the Johnson-Cook flow law for the P20 steel.}
\begin{tabular}{ccccc}
\hline
$A~(\text{MPa})$ & $B~(\text{MPa})$ & $n$ & $C$ & $m$\\
$11.758$ & $25.563$ &  $0.139$ & $0.338$ & $0.730$\\ \hline
\label{tab:JCparams}
\end{tabular}
\end{table}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]{Figures/CompExpJC}
\caption{Comparison between the experimental and predicted flow stresses by JC model.}
\label{fig:iCorrelationJC}
\end{figure}

@@

Considering the expression of the model given by Equation (\ref{eq:MZA-model}), parameter $C_1$ is deduced direcly from $\sigma^y(\varepsilon^p=0,T=T_0,\mdot\varepsilon=\mdot{\varepsilon}_0)$. When the current strain rate $\mdot\varepsilon$ is identical to the reference strain rate $\mdot{\varepsilon}_0$, the Equation (\ref{eq:MZA-model}) becomes :
\begin{equation}
\sigma^y = \left(C_{1}+C_{2}\varepsilon^{p^n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right)\right]
\end{equation}
Taking the logarithm of the previous relationship we have :
\begin{equation}
\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right)-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right)
\end{equation}
By plotting the function $\ln\sigma^y\left(T-T_0\right)$ the y-intercept and the slope of this line can be deduced as $I_1=\ln\left(C_1+C_2\varepsilon^{p^n}\right)$ and $S_1=-\left(C_3+C_4\varepsilon^p\right)$.
From the expression of $I_1$ we can write:
\begin{equation}
\ln\left(\exp(I_1)-C_1\right) = \ln C_2+n\ln\varepsilon^p
\end{equation}
By plotting the function $\ln\left(\exp(I_1)-C_1\right)$ versus $\ln\varepsilon^p$ we can deduce $n$ and $C_2$. The plot of $S_1$ versus $\varepsilon^p$ allows deducing $C_3$ and $C_4$ from the y-intercept and the slope, respectively. Once the first four terms of the model are calculated, we can now take the logarithm of the entire MZA model given by Equation (\ref{eq:MZA-model}).
\begin{equation}
\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right) - \left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + S_2\ln\left( \frac{\mdot\varepsilon}{\mdot{\varepsilon}_0}\right)
\end{equation}
with $S_2=C_5+C_6\left(T-T_0\right)$. Finally, the graph $\ln\sigma^y$ versus $ \ln(\mdot\varepsilon/\mdot{\varepsilon}_0)$ allows deducing $C_5$ and $C_6$ from the slope $S_2$. The parameters of MZA model are given in the Table \ref{tab: MZAparameters} while its prediction are shown in Figure \ref{fig:iCorrelationMZA}. It can be seen from those figures that the MZA model as JC model is not suitable to describe experimental at low strain rates but much better for high strain rates. The deviation between the predicted values and the experimental values is large because this model has problem to correctly describe the softening in its formulation. That is aspect of the limitations of that model as presented in \cite{TizeMha-2022}.
\begin{table}[h!]
\centering{}
\caption{Parameters' constants of Modified-Zerilli-Armstrong Model}
\begin{tabular}{llllllc}
\hline
$C_1(\text{MPa})$    &$C_2(\text{MPa})$        & $C_3(\times10^{-5})$     & $C_4(\times10^{-5})$   & $C_5(\times10^{-5})$       &$C_6(\times10^{-5})$&$n$\\
$43.0988$&$112.975$& $330.976$&$4.27581$&$14106.3$&$17.4178$&$0.305028$\\
\hline
\label{tab: MZAparameters}
\end{tabular}
\end{table}
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{Figures/CompExpMZA}
\caption{Comparison between the experimental and predicted flow stresses by MZA model}
\label{fig:iCorrelationMZA}
\end{figure}
\FloatBarrier

@@

\begin{table}[h!]
\centering
\caption{Parameters' values of the Hansel-Spittel flow law for the P20 steel.}
\begin{tabular}{ccccc}
\hline
$A~(\text{MPa})$ & $m_1$ & $m_2$ & $m_3$ & $m_4$\\
$5954.043$ & $-3.358\times10^{-3}$ & $2.641\times10^{-1}$ & $-8.678\times10^{-2}$ & $2.269\times10^{-4}$\\\hline
& $m_5$ & $m_6$ & $m_7$ & $m_8$\\
& $-4.216\times10^{-4}$ & $-5.613\times10^{-2}$ & $2.264\times10^{-4}$ & $0$\\\hline
\label{tab:HSparameters}
\end{tabular}
\end{table}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{Figures/CompExpHS}
\caption{Comparison between the experimental and predicted flow stresses by HS model}
\label{fig:iCorrelationHS}
\end{figure}

@@

The determination of the order $m$ of the polynomials defined by Equations (\ref{eq:ArA}-\ref{eq:Arn}) is defined according to the ability of the model to represent the non-linear dependence of the stress versus the strain and its generalization.
The values $\ln\!A_i$, $\alpha_i$, $n_i$, and $Q_i$ ($i=1,2,3,\cdots,m$) are the coefficients of the polynomials to determine using a regression method.
Setting $m=9$ gives the best results and the corresponding parameters are reported in Table \ref{tab:ARparameters}.
\begin{table}[h!]
\centering
\caption{Parameters' values of the Arrhenius flow law for the P20 steel}
\begin{tabular}{llll}
\hline
\multicolumn{1}{c}{$\alpha_i~(\text{MPa}^{-1})$} & \multicolumn{1}{c}{$Q_i~(\text{MJ.mol}^{-1})$} & \multicolumn{1}{c}{$\ln\!A_i~(\ps)$} & \multicolumn{1}{c}{$n_i$}\\
\hline
$\alpha_0=0.0392$ & $Q_0=0.467$ & $\ln\!A_0=35.8092$ & $n_0=4.8216$ \\
$\alpha_1=-0.4092$ & $Q_1=-0.6516$ & $\ln\!A_1=-58.8219$ & $n_1=3.2813$ \\
$\alpha_2=3.9229$ & $Q_2=7.6084$ & $\ln\!A_2=740.3302$ & $n_2=71.5963$ \\
$\alpha_3=-20.713$ & $Q_3=-48.016$ & $\ln\!A_3=-5049.2979$ & $n_3=-1956.1871$ \\
$\alpha_4=62.1376$ & $Q_4=66.795$ & $\ln\!A_4=11305.3573$ & $n_4=14460.9217$ \\
$\alpha_5=-99.9999$ & $Q_5=468.8898$ & $\ln\!A_5=20220.008$ & $n_5=-54309.8814$ \\
$\alpha_6=58.7108$ & $Q_6=-2303.1535$ & $\ln\!A_6=-153871.1135$ & $n_6=117612.0374$ \\
$\alpha_7=54.3688$ & $Q_7=4370.6566$ & $\ln\!A_7=317981.5396$ & $n_7=-148819.8996$ \\
$\alpha_8=-99.9999$ & $Q_8=-3939.3826$ & $\ln\!A_8=-297254.899$ & $n_8=102387.2537$ \\
$\alpha_9=42.5233$ & $Q_9=1397.0283$ & $\ln\!A_9=107585.17$ & $n_9=-29621.1293$ \\
\hline
\label{tab:ARparameters}
\end{tabular}
\end{table}
This modified form of the Arrhenius behavior law allows for accurate and reliable prediction over a wide range of temperatures and strain rates.
Equation (\ref{eq:ArStress}) is finally used to compute the flow stress $\sigma^y$ from the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$:
\begin{equation}
\sigma^y = \frac{1}{\alpha(\varepsilon)} \ln\left\{\left(\frac{\mdot\varepsilon \exp{\left(\frac{Q(\varepsilon)}{RT}\right)}}{A(\varepsilon)}\right)^{\frac{1}{n(\varepsilon)}} + \left[1 + \left(\frac{\mdot\varepsilon \exp{\left(\frac{Q(\varepsilon)}{RT}\right)}}{A(\varepsilon)}\right)^{\frac{2}{n(\varepsilon)}}\right]^{\frac{1}{2}}\right\}
\label{eq:ArStress}
\end{equation}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{Figures/CompExpAR}
\caption{Comparison between the experimental and predicted flow stresses by AR model}
\label{fig:iCorrelationAR}
\end{figure}

@@

\begin{table}[h!]
\centering
\caption{Parameters' values of the PTM flow law for the P20 steel}
\begin{tabular}{llll}
\hline
\multicolumn{1}{c}{$A_i$} & \multicolumn{1}{c}{$B_i$} & \multicolumn{1}{c}{$C_0^i$} & \multicolumn{1}{c}{$C_1^i$}\\
\hline
$A_0=16.8528$ & $B_0=-0.0035$ & $C_0^0=0.1607$ & $C_1^0=0.0$\\
$A_1=340.6451$ & $B_1=-0.0131$ & $C_0^1=-0.6201$ & $C_1^1=0.0026$\\
$A_2=-1959.4041$ & $B_2=-0.0044$ & $C_0^2=4.9515$ & $C_1^2=-0.0035$\\
$A_3=4835.9698$ & $B_3=0.2217$ & $C_0^3=-13.1693$ & $C_1^3=-0.0222$\\
$A_4=-5517.6094$ & $B_4=-0.4988$ & $C_0^4=15.2499$ & $C_1^4=0.0608$\\
$A_5=2405.8399$ & $B_5=0.3211$ & $C_0^5=-6.5869$ & $C_1^5=-0.0412$\\
\hline
\label{tab:PTM-parameters}
\end{tabular}
\end{table}

\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{Figures/CompExpPTM}
\caption{Comparison between the experimental and predicted flow stresses by PTM model }
\label{fig:iCorrelationPTM}
\end{figure}
\FloatBarrier

@@

In this study $700$ of data were used; $80\%$ (560) are randomly selected for training and $20\%$ (140) for testing. Before learning, a normalisation of the data is required in order to have all data between $0$ and $1$. The Equation is widely used for normalization.
\begin{equation}
X_n = \frac{X - X_{min}}{X_{max} - X_{min}}
\end{equation}
Where $X$ is the orginal data ($\varepsilon^p$, $\log(\mdot\varepsilon/\varepsilon_0$,  $T$, $\sigma^y$), $X_{min}$ and $X_{max}$ are the minimum and maximum values of $X$ respectively. $X_n$ is the normalized data of the corresponding $X$. The trained model once tested can be used to predict the behavior of the AISI P20 alloy. Figure \ref{fig:iCorrelationANN} show a comparison between the predicted ﬂow stresses from ANN model and measured data from hot compression test. As shown from this figures, the correlation between the experimental and the ANN prediction based is very good over the full range of data and the predicted data can well track the hardening and softening regions of the hot deforming material. Therefore, the ANN model can be used to simulate the hot deformation of this type of alloy. This was not necessarily the case with the analytical models. The performance of this prediction will be much more appreciated when it comes to testing its ability to predict data that has not been used in either the training or the test data, but rather a full-fledged trial that we wish to validate the ANN prediction by experimental. This validation will be done both with a strain rate between and outside of those used for the training step.
\begin{figure}[!ht]
\centering
\includegraphics[width=1\columnwidth]
{Figures/CompExpANN}
\caption{Comparison between the experimental and predicted flow stresses by ANN model }
\label{fig:iCorrelationANN}
\end{figure}
\FloatBarrier
%-------------------------------------------------------------------------
\subsection{Comparison of analytical and ANN models\label{sec:Comparison}}
%--------------------------------------------------------------------------
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{Figures/Correlation}
\caption{Correlation coefficient ($R$) of models developed}
\label{fig:Correlation}
\end{figure}
The accuracy and predictive ability of both analytical and ANN models are generally assessed by some coefficients such as the correlation coefﬁcient ($R$) (Equation (\ref{eq:R-expression})), Average Absolute Relative Error ($\AARE$ generally known as $\AARE$) (Equation (\ref{eq:AARE-expression})) and Root Mean Square Error ($\RMSE$) (Equation (\ref{eq:RMSE-expression})).
\begin{equation}
\label{eq:R-expression}
\R(\%) = \frac{\displaystyle\sum_{i=1}^{N}{\left(E_i - \overline{E}\right)\left(P_i - \overline{P}\right)}}{\sqrt{\displaystyle\sum_{i=1}^{N}\left(E_i - \overline{E}\right)^2 .\displaystyle\sum_{i=1}^{N}\left(P_i - \overline{P}\right)^2}}\times 100
\end{equation}
\begin{equation}
\label{eq:AARE-expression}
\AARE(\%) = \frac{1}{N}\displaystyle\sum_{i=1}^{N} \displaystyle\left\lvert\frac{E_i- P_i}{E_i} \right\rvert\times 100
\end{equation}
\begin{equation}
\label{eq:RMSE-expression}
\RMSE (\text{MPa}) = \sqrt{\frac{1}{N} \displaystyle\sum_{i=1}^{N} \left(E_i - P_i\right)^2}
\end{equation}
Where $E_i$ is the experimental value and $P_i$ is the predicted value of the constitutive law (phenomenological and ANN models), $\overline{E}$ and $\overline{P}$ are the mean values of the experimental and predicted values, respectively.

@@

In this section we wish to test the performance of each identified model data interpolating and extrapolating data. Indeed, out of the $6$ strain rates used, one strain rate is voluntarily removed (while keeping the same values of strains and temperatures used for the development of the phenomenological and ANN models) so that it is inside or outside the other $5$ strain rates. For the strain rate which is between the minimum and the maximum of the $5$ other strain rates, we will thus test the capacity of each model to interpolate the data and for the one which is out of the $5$ other strain rates, the extrapolation capacity of the model is therefore validated. The validation procedure is as follows: $5$ strain rates are used to re-identify each model and once identified, it is used to predict the flow stress for the strain rate chosen for both interpolation and extrapolation. Validation is done with real data. The following subsections will highlight this procedure.

@@

For the validation of the interpolation, the chosen strain rate is $\mdot\varepsilon = 1.0\ \ps$ and those used for identification (training for ANN) are $\mdot\varepsilon = 0.001\ \ps$ , $\mdot\varepsilon = 0.01\ \ps$ , $\mdot\varepsilon = 0.1\ \ps$, $\mdot\varepsilon = 2.0\ \ps$  and $\mdot\varepsilon = 5.0\ \ps$. The Figure \ref{fig:inCombinaison} shows the comparison between the predictions of the analytical and ANN models and the experiment. It appears from these Figures that all models have relatively good predictions but the ANN model remains the best because the value of its $\AARE$ is $1.4\%$ while it is between $2.33\%$ and $6.13\%$ for the analytical models. This further shows the performance of the ANN model compared to the analytical models. All these results are summarized in Table \ref{tab:inValid}.

@@

For the validation of the extrapolation, the chosen strain rate is $\mdot\varepsilon = 5.0\ \ps$ and those used for identification (training for ANN) are $\mdot\varepsilon = 0.001\ \ps$ , $\mdot\varepsilon = 0.01\ \ps$ , $\mdot\varepsilon = 0.1\ \ps$, $\mdot\varepsilon = 1.0\ \ps$  and $\mdot\varepsilon = 2.0\ \ps$. Figure \ref{fig:exCombinaison} shows the comparison between the predictions  and the experimental. Unlike interpolation, the predictions of the analytical models are not very good because the errors are between $3.2\%$ and $12.99\%$ while that of the ANN model is $1.74\%$. Again, the ANN model shows its ability to extrapolate data. This makes it possible to say that the ANN model remains the best tool to characterize the behavior of a material subjected to certain deformation conditions. It can also be noted that the Arhenius and the PTM models still have some ability to extrapolate because their $\AARE$ are respectively $ 3.2 \% $ and $ 3.8 \%$; which are acceptable.

>>>>

The procedure used for the determination of the parameters of the Johnson-Cook law is in accordance with the one proposed by He \eal \cite{He-2013}.
This method allows obtaining one after the other the $5$ parameters in the order $A$, $B$, $n$, $C$ and $m$.
Thus, according to the experimental data, the initial elastic limit of the material at the reference strain rate and reference temperature is $A=13.5143$~MPa.
For the determination of the constants $B$ and $n$, from the results of the compression test at $T_0$ and $\mdot\varepsilon_0$, it is then possible to determine these two constants by considering only the first term $\left(A+B\varepsilon^{p^{n}}\right)$ in Equation (\ref{eq:Johnson-Cook}).
Thus, here, $B=21.816$~MPa and $n=0.0746$.
Once the parameters $A$, $B$ and $n$ are known, the determination of $C$, considering all the curves at $T=T_0$ then gives $C=0.3404$.
Finally, the last parameter $m$ is identified from the curves at $\mdot\varepsilon=\mdot\varepsilon_0$ and from the knowledge of the previous and gives $m=0.7057$.
All parameters of the Johnson-Cook model are reported in Table \ref{tab:JCparams}.

\begin{table}[h!]
\centering
\caption{Parameters' values of the Johnson-Cook flow law for the P20 steel.}
\begin{tabular}{ccccc}
\hline
$A~(\text{MPa})$ & $B~(\text{MPa})$ & $n$ & $C$ & $m$\\
$13.5143$&$21.816$&$0.0746$&$0.3404$&$0.7057$\\ \hline
\label{tab:JCparams}
\end{tabular}
\end{table}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]{Figures/CompExp-JC-6}
\caption{Comparison between the experimental and predicted flow stresses by JC model.}
\label{fig:iCorrelationJC}
\end{figure}

@@

Considering the expression of the model given by Equation (\ref{eq:MZA-model}), parameter $C_1$ is deduced direcly from $\sigma^y(\varepsilon^p=0,T=T_0,\mdot\varepsilon=\mdot{\varepsilon}_0)$.
When the current strain rate $\mdot\varepsilon$ is identical to the reference strain rate $\mdot{\varepsilon}_0$, the Equation (\ref{eq:MZA-model}) becomes :
\begin{equation}
\sigma^y = \left(C_{1}+C_{2}\varepsilon^{p^n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right)\right]
\end{equation}
Taking the logarithm of the previous relationship we have :
\begin{equation}
\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right)-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right)
\end{equation}
By plotting the function $\ln\sigma^y\left(T-T_0\right)$ the y-intercept and the slope of this line can be deduced as $I_1=\ln\left(C_1+C_2\varepsilon^{p^n}\right)$ and $S_1=-\left(C_3+C_4\varepsilon^p\right)$.
From the expression of $I_1$ we can write:
\begin{equation}
\ln\left(\exp(I_1)-C_1\right) = \ln C_2+n\ln\varepsilon^p
\end{equation}
By plotting the function $\ln\left(\exp(I_1)-C_1\right)$ versus $\ln\varepsilon^p$ we can deduce $n$ and $C_2$.
The plot of $S_1$ versus $\varepsilon^p$ allows deducing $C_3$ and $C_4$ from the y-intercept and the slope, respectively.
Once the first four terms of the model are calculated, we can now take the logarithm of the entire MZA model given by Equation (\ref{eq:MZA-model}).
\begin{equation}
\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right) - \left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + S_2\ln\left( \frac{\mdot\varepsilon}{\mdot{\varepsilon}_0}\right)
\end{equation}
with $S_2=C_5+C_6\left(T-T_0\right)$.
Finally, the graph $\ln\sigma^y$ versus $ \ln(\mdot\varepsilon/\mdot{\varepsilon}_0)$ allows deducing $C_5$ and $C_6$ from the slope $S_2$.
The parameters of MZA model are given in the Table \ref{tab: MZAparameters} while its prediction are shown in Figure \ref{fig:iCorrelationMZA}.
It can be seen from those figures that the MZA model as JC model is not suitable to describe experimental at low strain rates but much better for high strain rates.
The deviation between the predicted values and the experimental values is large because this model has problem to correctly describe the softening in its formulation.
That is aspect of the limitations of that model as presented in \cite{TizeMha-2022}.
\begin{table}[h!]
\centering{}
\caption{Parameters' constants of Modified-Zerilli-Armstrong Model}
\begin{tabular}{ccccccc}
\hline
$C_1$ & $C_2$ & $C_3$ & $C_4$ & $C_5$ & $C_6$ & $n$\\
$13.5143$ & $21.2591$ & $4.7902\times 10^{-3}$ & $1.4895\times 10^{-4}$ & $0.1389$ & $1.495\times 10^{-4}$ & $0.0621$\\
\hline
\label{tab: MZAparameters}
\end{tabular}
\end{table}
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{Figures/CompExp-MZA-6}
\caption{Comparison between the experimental and predicted flow stresses by MZA model}
\label{fig:iCorrelationMZA}
\end{figure}
\FloatBarrier

@@

\begin{table}[h!]
\centering
\caption{Parameters' values of the Hansel-Spittel flow law for the P20 steel.}
\begin{tabular}{ccccc}
\hline
$A$ & $m_1$ & $m_2$ & $m_3$ & $m_4$\\
$5.954\times 10^{3}$ & $-3.3576\times10^{-3}$ & $0.2641$ & $-0.0868$ & $2.2688\times10^{-4}$\\\hline
& $m_5$ & $m_6$ & $m_7$ & $m_8$\\
& $-4.2163\times10^{-4}$ & $-0.0561$ & $2.264\times10^{-4}$ & $0$\\\hline
\label{tab:HSparameters}
\end{tabular}
\end{table}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{Figures/CompExp-HS-6}
\caption{Comparison between the experimental and predicted flow stresses by HS model}
\label{fig:iCorrelationHS}
\end{figure}

@@

The determination of the order $m$ of the polynomials defined by Equations (\ref{eq:ArA}-\ref{eq:Arn}) is defined according to the ability of the model to represent the non-linear dependence of the stress versus the strain and its generalization.
The values $\ln\!A_i$, $\alpha_i$, $n_i$, and $Q_i$ ($i=1,2,3,\cdots,m$) are the coefficients of the polynomials to determine using a regression method.
Setting $m=9$ gives the best results and the corresponding parameters are reported in Table \ref{tab:ARparameters}.
\begin{table}[h!]
\centering
\caption{Parameters' values of the Arrhenius flow law for the P20 steel}
\begin{tabular}{llll}
\hline
\multicolumn{1}{c}{$\alpha_i$} & \multicolumn{1}{c}{$Q_i~(\times 10^{-6})$} & \multicolumn{1}{c}{$\ln\!A_i$} & \multicolumn{1}{c}{$n_i$}\\
\hline
$\alpha_0=0.0407$ & $Q_0=0.467$ & $A_0=35.8092$ & $n_0=4.8217$\\
$\alpha_1=-0.5167$ & $Q_1=-0.6517$ & $A_1=-58.822$ & $n_1=3.2814$\\
$\alpha_2=6.3912$ & $Q_2=7.6084$ & $A_2=740.3303$ & $n_2=71.5963$\\
$\alpha_3=-47.3364$ & $Q_3=-48.016$ & $A_3=-5.0493\times 10^{3}$ & $n_3=-1.9562\times 10^{3}$\\
$\alpha_4=220.0014$ & $Q_4=66.795$ & $A_4=1.1305\times 10^{4}$ & $n_4=1.4461\times 10^{4}$\\
$\alpha_5=-654.4553$ & $Q_5=468.8898$ & $A_5=2.022\times 10^{4}$ & $n_5=-5.431\times 10^{4}$\\
$\alpha_6=1.2421\times 10^{3}$ & $Q_6=-2.3032\times 10^{3}$ & $A_6=-1.5387\times 10^{5}$ & $n_6=1.1761\times 10^{5}$\\
$\alpha_7=-1.4523\times 10^{3}$ & $Q_7=4.3707\times 10^{3}$ & $A_7=3.1798\times 10^{5}$ & $n_7=-1.4882\times 10^{5}$\\
$\alpha_8=952.0619$ & $Q_8=-3.9394\times 10^{3}$ & $A_8=-2.9725\times 10^{5}$ & $n_8=1.0239\times 10^{5}$\\
$\alpha_9=-267.4994$ & $Q_9=1.397\times 10^{3}$ & $A_9=1.0759\times 10^{5}$ & $n_9=-2.9621\times 10^{4}$\\
\hline
\label{tab:ARparameters}
\end{tabular}
\end{table}
This modified form of the Arrhenius behavior law allows for accurate and reliable prediction over a wide range of temperatures and strain rates.
Equation (\ref{eq:ArStress}) is finally used to compute the flow stress $\sigma^y$ from the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$:
\begin{equation}
\sigma^y = \frac{1}{\alpha(\varepsilon)} \ln\left\{\left(\frac{\mdot\varepsilon \exp{\left(\frac{Q(\varepsilon)}{RT}\right)}}{A(\varepsilon)}\right)^{\frac{1}{n(\varepsilon)}} + \left[1 + \left(\frac{\mdot\varepsilon \exp{\left(\frac{Q(\varepsilon)}{RT}\right)}}{A(\varepsilon)}\right)^{\frac{2}{n(\varepsilon)}}\right]^{\frac{1}{2}}\right\}
\label{eq:ArStress}
\end{equation}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{Figures/CompExp-AR-6}
\caption{Comparison between the experimental and predicted flow stresses by AR model}
\label{fig:iCorrelationAR}
\end{figure}

@@

\begin{table}[h!]
\centering
\caption{Parameters' values of the PTM flow law for the P20 steel}
\begin{tabular}{llll}
\hline
\multicolumn{1}{c}{$A_i$} & \multicolumn{1}{c}{$B_i$} & \multicolumn{1}{c}{$C_0^i$} & \multicolumn{1}{c}{$C_1^i$}\\
\hline
$A_0=16.8529$ & $B_0=-3.5418\times 10^{-3}$ & $C_0^0=0.1608$ & $C_1^0=-1.9037\times 10^{-5}$\\
$A_1=340.6451$ & $B_1=-0.0132$ & $C_0^1=-0.6202$ & $C_1^1=2.67\times 10^{-3}$\\
$A_2=-1.9594\times 10^{3}$ & $B_2=-4.4888\times 10^{-3}$ & $C_0^2=4.9516$ & $C_1^2=-3.5788\times 10^{-3}$\\
$A_3=4.836\times 10^{3}$ & $B_3=0.2218$ & $C_0^3=-13.1694$ & $C_1^3=-0.0222$\\
$A_4=-5.5176\times 10^{3}$ & $B_4=-0.4988$ & $C_0^4=15.25$ & $C_1^4=0.0609$\\
$A_5=2.4058\times 10^{3}$ & $B_5=0.3211$ & $C_0^5=-6.587$ & $C_1^5=-0.0413$\\
\hline
\label{tab:PTM-parameters}
\end{tabular}
\end{table}

\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{Figures/CompExp-PTM-6}
\caption{Comparison between the experimental and predicted flow stresses by PTM model}
\label{fig:iCorrelationPTM}
\end{figure}
\FloatBarrier

@@

In this study $700$ of data were used; $80\%$ (560) are randomly selected for training and $20\%$ (140) for testing.
Before learning, a normalisation of the data is required in order to have all data between $0$ and $1$.
The Equation is widely used for normalization.
\begin{equation}
X_n = \frac{X - X_{min}}{X_{max} - X_{min}}
\end{equation}
Where $X$ is the orginal data ($\varepsilon^p$, $\log(\mdot\varepsilon/\varepsilon_0$,  $T$, $\sigma^y$), $X_{min}$ and $X_{max}$ are the minimum and maximum values of $X$ respectively.
$X_n$ is the normalized data of the corresponding $X$.
The trained model once tested can be used to predict the behavior of the AISI P20 alloy.
Figure \ref{fig:iCorrelationANN} show a comparison between the predicted ﬂow stresses from ANN model and measured data from hot compression test.
As shown from this figures, the correlation between the experimental and the ANN prediction based is very good over the full range of data and the predicted data can well track the hardening and softening regions of the hot deforming material.
Therefore, the ANN model can be used to simulate the hot deformation of this type of alloy.
This was not necessarily the case with the analytical models.
The performance of this prediction will be much more appreciated when it comes to testing its ability to predict data that has not been used in either the training or the test data, but rather a full-fledged trial that we wish to validate the ANN prediction by experimental.
This validation will be done both with a strain rate between and outside of those used for the training step.
\begin{figure}[!ht]
\centering
\includegraphics[width=1\columnwidth]
{Figures/CompExp-3-15-7-1-sigmoid}
\caption{Comparison between the experimental and predicted flow stresses by the 3-15-7-1-sigmoid ANN model}
\label{fig:iCorrelationANN}
\end{figure}
\FloatBarrier
%-------------------------------------------------------------------------
\subsection{Comparison of analytical and ANN models\label{sec:Comparison}}
%--------------------------------------------------------------------------

The accuracy and predictive ability of both analytical and ANN models are generally assessed by some coefficients such as the correlation coefﬁcient ($R$) (Equation (\ref{eq:R-expression})), Average Absolute Relative Error ($\AARE$ generally known as $\AARE$) (Equation (\ref{eq:AARE-expression})) and Root Mean Square Error ($\RMSE$) (Equation (\ref{eq:RMSE-expression})).
\begin{equation}
\label{eq:R-expression}
\R(\%) = \frac{\displaystyle\sum_{i=1}^{N}{\left(E_i - \overline{E}\right)\left(P_i - \overline{P}\right)}}{\sqrt{\displaystyle\sum_{i=1}^{N}\left(E_i - \overline{E}\right)^2 .\displaystyle\sum_{i=1}^{N}\left(P_i - \overline{P}\right)^2}}\times 100
\end{equation}
\begin{equation}
\label{eq:AARE-expression}
\AARE(\%) = \frac{1}{N}\displaystyle\sum_{i=1}^{N} \displaystyle\left\lvert\frac{E_i- P_i}{E_i} \right\rvert\times 100
\end{equation}
\begin{equation}
\label{eq:RMSE-expression}
\RMSE (\text{MPa}) = \sqrt{\frac{1}{N} \displaystyle\sum_{i=1}^{N} \left(E_i - P_i\right)^2}
\end{equation}
Where $E_i$ is the experimental value and $P_i$ is the predicted value of the constitutive law (phenomenological and ANN models), $\overline{E}$ and $\overline{P}$ are the mean values of the experimental and predicted values, respectively.

@@

In this section we wish to test the performance of each identified model data interpolating and extrapolating data.
Indeed, out of the $6$ strain rates used, one strain rate is voluntarily removed (while keeping the same values of strains and temperatures used for the development of the phenomenological and ANN models) so that it is inside or outside the other $5$ strain rates.
For the strain rate which is between the minimum and the maximum of the $5$ other strain rates, we will thus test the capacity of each model to interpolate the data and for the one which is out of the $5$ other strain rates, the extrapolation capacity of the model is therefore validated.
The validation procedure is as follows: $5$ strain rates are used to re-identify each model and once identified, it is used to predict the flow stress for the strain rate chosen for both interpolation and extrapolation.
Validation is done with real data.
The following subsections will highlight this procedure.

@@

For the validation of the interpolation, the chosen strain rate is $\mdot\varepsilon = 1.0\ \ps$ and those used for identification (training for ANN) are $\mdot\varepsilon = 0.001\ \ps$ , $\mdot\varepsilon = 0.01\ \ps$ , $\mdot\varepsilon = 0.1\ \ps$, $\mdot\varepsilon = 2.0\ \ps$  and $\mdot\varepsilon = 5.0\ \ps$.
The Figure \ref{fig:inCombinaison} shows the comparison between the predictions of the analytical and ANN models and the experiment.
It appears from these Figures that all models have relatively good predictions but the ANN model remains the best because the value of its $\AARE$ is $1.4\%$ while it is between $2.33\%$ and $6.13\%$ for the analytical models.
This further shows the performance of the ANN model compared to the analytical models.
All these results are summarized in Table \ref{tab:inValid}.

@@

For the validation of the extrapolation, the chosen strain rate is $\mdot\varepsilon = 5.0\ \ps$ and those used for identification (training for ANN) are $\mdot\varepsilon = 0.001\ \ps$ , $\mdot\varepsilon = 0.01\ \ps$ , $\mdot\varepsilon = 0.1\ \ps$, $\mdot\varepsilon = 1.0\ \ps$  and $\mdot\varepsilon = 2.0\ \ps$.
Figure \ref{fig:exCombinaison} shows the comparison between the predictions  and the experimental.
Unlike interpolation, the predictions of the analytical models are not very good because the errors are between $3.2\%$ and $12.99\%$ while that of the ANN model is $1.74\%$.
Again, the ANN model shows its ability to extrapolate data.
This makes it possible to say that the ANN model remains the best tool to characterize the behavior of a material subjected to certain deformation conditions.
It can also be noted that the Arhenius and the PTM models still have some ability to extrapolate because their $\AARE$ are respectively $ 3.2 \% $ and $ 3.8 \%$; which are acceptable.
